From Education To Entrepreneurship

### 2014-11-29 FromEducationToEntrepreneurship.Rmd
Editing Literature Review 2

What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors. Still, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007]. Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done, as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.

@@

Also, as self-confidence is considered to rely partly on one’s integration within social networks [@OECD2009], we will refer to cross-cultural studies such as that of Green, Deschamps and Páez [@green2005variation] about individualism and collectivism, what Freeman [@freeman1997demographic] called idiocentrism and allocentrism. Raeff, Greenfield and Quiroz [-@raeff2000conceptualizing] have also conceptualized interpersonal relationships in both contexts. More school-focused, Yamauchi [@yamauchi1998individualism] as well as Davies and Aurini [@davies2003homeschooling] have looked at individualism and collectivism in the classroom and in pedagogy respectively. All these will be important on the way.

Besides direct or indirect school effects, we will necessarily look into entrepreneurship and its determinants at large. Thus we will quote Grilo and Thurik’s research [@Grilo2005b] about what determines entrepreneurship engagement levels throughout the European Union, and also Wennekers Sander, Ulhaner Lorraine and Thurik Roy’s explanation of variation across countries [@Wennekers2002]. Eventually, with Gartner [@Gartner1990] we will have a closer look at entrepreneurship’s underlying meanings in research and, along with Acs, Desai and Klapper [@Acs2008], we will ask ourselves what “entrepreneurship” data really shows.

>>>>

What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors. Still, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] ?????? 2010 VERSION MAIN BIB ?????. Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done, as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.

@@

Further, since self-confidence is considered to rely partly on one’s integration within social networks [@OECD2009], we will refer to cross-cultural studies about individualism and collectivism such as those of Green, Deschamps and Páez [@green2005variation], Pinillos and Reyes ???????? MAIN BIB ??????, Freeman [@freeman1997demographic], Raeff, Greenfield and Quiroz [-@raeff2000conceptualizing]. We will also cite more school-focused research like Yamauchi [@yamauchi1998individualism], Davies and Aurini [@davies2003homeschooling] for these have looked at individualism and collectivism in the classroom and in pedagogy respectively.

Besides potential educational effects on self-confidence and social capital, we will need to control for all classic entrepreneurship determinants. Therefore, we will quote Grilo and Thurik’s research [@Grilo2005b] about what determines entrepreneurship engagement levels throughout the European Union and the US, Wennekers, Ulhaner and Thurik’s about variation across countries [@Wennekers2002], Freytag and Thurik about determinants in a cross-country setting ????? 2010 VERSION MAINBIB ?????.

Eventually, to put all these into perspective, along with Gartner [@Gartner1990] we will have a closer look at entrepreneurship’s underlying meanings in research and, with Acs, Desai and Klapper [@Acs2008], we will ask ourselves what “entrepreneurship” data really shows.
